### 2021-04-06 Chapter-2/Chapter-2.tex
Updates from Overleaf

The first side-channel attack of cryptography libraries can be traced back to Kocher's timing attacks~\cite{kocher1996timing} in 1996. It exploits the the simple modular exponentiation algorithm function in many algorithms (Diffie-Helloman, RSA) implementations. The function does not run in a fixed time. By measuring the time differences between the modular exponentiation algorithm computes the exponent bits (0 or 1), Kocher's attack can recover the whole secret key bit by bit. Since then, researchers start to break all kinds of cipher implementation through side-channel attacks.  Table~\ref{chapter2:table:crypto} summarizes some common vulnerable points in cryptography library implementations.  Note that Cryptography libraries usually have several implementations for some symmetric ciphers.
For example, AES can have more than five different implementations  in OpenSSL. Depending on the build configuration and the return value of \textsf{CPUID}, the code may execute any implementation of them. The reference implementation usually adopts T-Tables and S-Tables to speed up the computation. However, such implementations are vulnerable to side-channels and can be exploited to retrieve the whole key~\cite{bonneau2006cache}. In addition to the reference implementation, those libraries also have side channel silent versions. However, recent studies also shows those versions also have side-channel vulnerabilities caused by compiler optimizations and human mistakes~\cite{217537}. The situation is even worse for asymmetric ciphers (e.g., Diffie-Helloman, RSA, ECDSA) because those those ciphers have a lots of big number calculations. It is hard to implement those calculations completely side-channel resistant. Recent work~\cite{arnaud2013timing,yarom2017cachebleed,yarom2014flush+} has demonstrated several end-to-end attacks to recover the private keys of those ciphers.
\subsubsection{Machine Learning Applications}
Recent side-channel attack on machine learning applications mainly focus on recovering two types of the sensitive information: the input of the model, and the architecture of deep learning models. Hua et al.~\cite{hua2018reverse} were the first in the literature to reverse engineer the architecture of convolutional neural networks (CNNs) through the memory access patterns. Wei et al.~\cite{wei2018know} perform the side-channel attacks on an FPG-based convolution neural network based on the power consumption to recover inputs to the networks. For an image classification task trained by the MNIST dataset, their attacks can achieve up 89\% accuracy. CSI NN~\cite{batina2019csi} reverse engineer the multi-layer perception and convolution neural network based on the electromagnetic signals (EMs). Cache Telepathy~\cite{yan2020cache} introduces the cache based side-channel attack to extract DNNs' architectures. We find that all existing approaches need a lot of domain knowledge and expertise to launch the attacks.
\subsubsection{Media and Graphic Libraries}
A few of recent work also studies the side-channel attacks in media and graphic libraries. In the controlled-channel attack~\cite{xu2015controlled}, Yuanzhong et al. demonstrate an attack to recover the outline of the image by exploiting the vulnerability in the inverse DCT function in libjpeg. Daimeng et al.~\cite{wang2019unveiling} present the cache attack in graphic libraries. Their approaches combine a machine learning approach. They use the machine learning to pick cache lines that can be exploitable to leak most information.
\subsubsection{Others}
Some other side-channel targets also include spell checking tools, and font libraries~\cite{xu2015controlled}. The attack to font libraries is essentially the same as the attack to the graphic library like GTK. By exploiting the differences of memory accesses when the program renders different characters, an attacker can recover parts of the original sensitive information. Other side-channel attacks target on the kernel of the operating system. One example is the to use the side-channel attacks to break the kernel address space randomization (KASLR).
Many exploits rely on the knowledge of the memory location of a certain kernel function. Since Linux 4.12, the kernel loads core kernel image and device drivers at random positions during the boot time. Jang et al.~\cite{jang2016breaking} rely on side-channels to reveal mapping status of each page. After that, they detect kernel modules with unique size signatures to break KASLR. The second example relies on the side-channel vulnerabilities~\cite{cao2019principled} inside kernels to infer the TCP sequence numbers, which can be used to hijack connections between the client and the server~\cite{cao2016off}.

@@

\textbf{Trace comparison.} If a program has two different execution traces under two different sensitive inputs, then attacker can distinguish the sensitive input by observing the execution trace. Therefore, we can conclude the program is vulnerable to side-channel attacks. The method is similar to UNIX tool \textsf{diff}. Moreover, the approach does not need to model or abstract the program's semantics. In general, the approach is quite fast. On the negative side, comparing the trace along can find the leakage, but it cannot find the complex relationship between the leakage site and the original buffer. For example, if two leakage sites leak the same information in the original buffer, those approaches cannot find out the two leakage sites are the same.

\textbf{Abstraction.} The second category of those tools belongs to the field of abstractions. Tools based on those approaches use the abstraction to generate approximations of the semantics of computer programs. After that, by analyzing the model, those tools can identify side-channel leakages. Comparing with the trace comparison approach, the method is more precise.

Those methods usually follow the below steps. Suppose a program $P$ has $k$ as the input, we can run symbolic execution on the top the victim program. So temporary values can be represented as math formulas. After that, we need to build a cache or memory access model and model the side-channel leakage as a math constraint. Then we use SMT solvers to find if there are two different secret inputs that can lead to access different locations in the memory or the cache. If so, then the program is vulnerable to side-channel attacks. Contrary to the trace comparison, the method is quite precise. Moreover, it can model multiple leakages precisely as the conjunction of those formulas. However, such approach has the following limitations.

\begin{itemize}
    \item Existing tools cannot not handle many instructions such as AVX, and SIMD instructions.  Most existing tools are research prototype or are implemented based on the research prototype. For many projects, the tool is only implemented to properly handle the benchmark in their papers. Second, many those tools rely on transferring those instructions into some intermediate languages. However, those intermediate languages do not support those architecture instructions.
    \item Today's solvers can not handle many complicated constraints, especially the conjunction of those constraints. Recent studies show existing solver have bugs when it deals with floating pointer calculations.
\end{itemize}

>>>>

The first side-channel attack to cryptography libraries can be traced back to Kocher's timing attacks~\cite{kocher1996timing} in 1996. It exploits the the simple modular exponentiation algorithm function in many algorithms (Diffie-Helloman, RSA) implementations. The function does not run in a fixed time. By measuring the time differences between the modular exponentiation algorithm computes the exponent bits (0 or 1), Kocher's attack can recover the whole secret key bit by bit. Since then, researchers start to break all kinds of cipher implementation through side-channel attacks.  Table~\ref{chapter2:table:crypto} summarizes some common vulnerable points in cryptography library implementations.  Note that Cryptography libraries usually have several implementations for some ciphers.
For example, AES can have more than five different implementations  in OpenSSL. Depending on the build configuration and the return value of \textsf{CPUID}, the code may execute any implementation of them. The reference implementation usually adopts T-Tables and S-Tables to speed up the computation. However, such implementations are vulnerable to side-channels and can be exploited to retrieve the whole key~\cite{bonneau2006cache}. In addition to the reference implementation, those libraries also have side-channel mitigated versions. However, recent studies also shows those versions (e.g., AES-NI) also have side-channel vulnerabilities caused by compiler optimizations and human mistakes~\cite{217537}. The situation is even worse for asymmetric ciphers (e.g., Diffie-Helloman, RSA, ECDSA), because those those ciphers have a lots of big number calculations. It is hard to implement those calculations completely side-channel resistant. Recent work~\cite{arnaud2013timing,yarom2017cachebleed,yarom2014flush+} has demonstrated several end-to-end attacks to recover the private keys of those ciphers. There are two common countermeasures to mitigate the side-channel attacks in cryptography libraries. The first approach is to adopt constant time operation when computing the secret data.  It is hard to migrate all the code into a constant time implementation. The second approach is to use blinding to reduce the information that can attacker can retrieve. However, the binding value can also be retrieved by an attacker through other attacks including side-channel attacks.

\subsubsection{Machine Learning Applications}
Recent side-channel attacks on machine learning applications mainly focus on recovering two types of the sensitive information: the input of the model, and the architecture of deep learning models. Hua et al.~\cite{hua2018reverse} were the first in the literature to reverse engineer the architecture of convolutional neural networks (CNNs) through the memory access patterns. Wei et al.~\cite{wei2018know} perform the side-channel attacks on an FPG-based convolution neural network based on the power consumption to recover inputs to the networks. For an image classification task trained by the MNIST dataset, their attacks can achieve up 89\% accuracy. CSI NN~\cite{batina2019csi} reverse engineer the multi-layer perception and convolution neural network based on the electromagnetic signals (EMs). Cache Telepathy~\cite{yan2020cache} introduces the cache based side-channel attack to extract DNNs' architectures. We find that all existing approaches need a lot of domain knowledge and expertise to launch the attacks.
\subsubsection{Media and Graphic Libraries}
A few of recent work also studies the side-channel attacks in media and graphic libraries. Gruss el at. shows an attack that can infer keystrokes by exploiting secret-dependent memory accesses in the GDK library. In the controlled-channel attack~\cite{xu2015controlled}, Yuanzhong et al. demonstrate an attack to recover the outline of the image by exploiting the vulnerability in the inverse DCT function in libjpeg. Daimeng et al.~\cite{wang2019unveiling} present the cache attack in graphic libraries. Their approaches combine a machine learning approach. They use the machine learning to pick cache lines that can be exploitable to leak most information.
\subsubsection{Others}
Some other side-channel targets also include spell checking tools, and font libraries~\cite{xu2015controlled}. The attack to font libraries is essentially the same as the attack to the graphic library like GTK. By exploiting the differences of memory accesses when the program renders different characters, an attacker can recover parts of the original sensitive information. Other side-channel attacks target on the OS's kernel. One example is the to use the side-channel attacks to break the kernel address space randomization (KASLR).
Many exploits rely on the knowledge of the memory location of a certain kernel function. Since Linux 4.12, the kernel loads core kernel image and device drivers at random positions during the boot time. Jang et al.~\cite{jang2016breaking} rely on side-channels to reveal mapping status of each page. After that, they detect kernel modules with unique size signatures to break KASLR. The second example relies on the side-channel vulnerabilities~\cite{cao2019principled} inside kernels to infer the TCP sequence numbers, which can be used to hijack connections between the client and the server~\cite{cao2016off}.

@@

\textbf{Trace comparison.} If a program has two different execution traces under two different sensitive inputs, then attackers can distinguish the sensitive input by observing the execution trace. Therefore, we can conclude the program is vulnerable to side-channel attacks. The method is similar to the UNIX tool \textsf{diff}.  The approach does not need to model or abstract the program's semantics. In general, the approach is quite fast. On the negative side, comparing the trace along can find the leakage, but it cannot find the complex relationship between the leakage site and the original buffer. For example, if two leakage sites leak the same information in the original buffer, those approaches cannot find out the two leakage sites are the same.

\textbf{Abstraction.} The second category of those tools belongs to the field of abstractions. Tools based on those approaches use the abstraction to generate approximations of the semantics of computer programs. After that, by analyzing the model, those tools can identify side-channel leakages. Compared with the trace comparison approach, the method is more precise.

Those methods usually follow the below steps. Suppose a program $P$ has $k$ as the input. Those approaches first retrieve the relationship between the $k$ and temperate values during the execution. After that, they should have a cache or memory access model and model the side-channel leakage as a math constraint. By using SMT solvers to find if two different secret inputs can lead to access to different locations in the memory or the cache, those approaches can determine if the program is vulnerable to side-channel attacks.
Contrary to the trace comparison, the method is quite precise. Moreover, it can model multiple leakages precisely as the conjunction of those formulas. However, such approaches have the following limitations.

\begin{itemize}
    \item Many tools can only analyze the source code or the intermediate representation level. However, side-channel are low-level problems in general.  Most existing tools are research prototype or are implemented based on the research prototype. For some projects, the tool is only implemented to handle the benchmark in their papers properly. 
    \item Today's solvers can not handle some complicated constraints, especially the conjunction of those constraints. Recent studies show existing solvers have bugs when it deals with floating pointer calculations.
\end{itemize}
